---
title: "Exploratory Analysis"
output:
  html_document: default
  html_notebook: default
---

```{r message=FALSE}
library(dplyr)
library(ggplot2)
library(nlme)
```

Starting data
```{r}
subject_demographic_data <- read.csv("dataOct20_2018.csv")
subject_data <- read.csv("fall18_oddballCP.csv") 

#This person was missing some of the trials
subject_data <- subject_data %>% filter(subject_id != "5b7a902e16aa440001697f84")
```

Different phases of the experiment
```{r}
phase1 <- subject_data %>% filter(test_part == "phase_one") %>% group_by(subject_id) %>% mutate(trial_number = 1:n())
test <- subject_data %>% filter(test_part != "phase_one") %>% group_by(subject_id) %>% mutate(trial_number = 1:n())
odd_ball <- subject_data %>% filter(test_part == "ob_test") %>% mutate(pair = case_when(
  pair_type == "be" ~ "be",
  pair_type == "wi1" ~ "wi",
  pair_type == "wi2" ~ "wi",
  pair_type == "irr1" ~ "irr",
  pair_type == "irr2" ~ "irr",
  pair_type == "irr3" ~ "irr"
)) %>% mutate(is_rel = ifelse(pair=="irr", FALSE, TRUE))  %>% group_by(subject_id) %>% mutate(trial_number = 1:n())
number_judge <- subject_data %>% filter(test_part == "nj_test") %>% group_by(subject_id) %>% mutate(trial_number = 1:n())
category_judge <- subject_data %>% filter(test_part == "ct_test") %>% group_by(subject_id) %>% mutate(trial_number = 1:n())
```

Just performance in phase one
```{r}
averaged_distance_trial <- phase1 %>% group_by(trial_number, rel_dim) %>% summarise(distance = mean(as.numeric(as.character(distance)))) %>% mutate(subject_id="average")

phase1 %>% ggplot(aes(x=trial_number, y=as.numeric(as.character(distance)), group=subject_id)) + 
  geom_line(color="steelblue") + 
  facet_grid(rel_dim ~ .) + scale_y_continuous(name="Distance") +
  xlab("Trial Number") + geom_line(data=averaged_distance_trial)
```

```{r}
reversals_sum <- phase1 %>% group_by(rel_dim) %>% summarize(mean_trials_to_8 = mean(trial_number), sd = sd(trial_number))
reversals_sum
```

```{r}
# See what the average distance is for the last trial (not done)
```


Performance in phase 2
```{r}
# Oddball task by trial
averaged_distance_oddball <- odd_ball %>% group_by(trial_number, pair_type, assigned_Condition) %>% summarise(distance = mean(as.numeric(as.character(distance)))) %>% mutate(subject_id= ifelse(assigned_Condition=="control", "average_control", "average_exp"))

odd_ball %>% group_by(subject_id, pair_type, assigned_Condition) %>% ggplot(aes(x=trial_number, y=as.numeric(as.character(distance)), group=subject_id, color=assigned_Condition)) + 
  geom_line(color="steelblue") + facet_grid(pair_type ~ .) + 
  scale_y_continuous(name="Distance", limits=c(0, .4)) + 
  geom_line(data=averaged_distance_oddball)
```

```{r}
#Oddball task distance by trial, collapse over pair types
averaged_distance_pair_oddball <- odd_ball %>% group_by(trial_number, pair, assigned_Condition) %>% summarise(distance = mean(as.numeric(as.character(distance)))) %>% mutate(subject_id= ifelse(assigned_Condition=="control", "average_control", "average_exp"))

odd_ball %>% group_by(subject_id, pair, assigned_Condition) %>% ggplot(aes(x=trial_number, y=as.numeric(as.character(distance)), group=subject_id, color=assigned_Condition)) + 
  geom_line(color="steelblue") + facet_grid(pair ~ .) + 
  scale_y_continuous(name="Distance", limits=c(0, .35)) + 
  geom_line(data=averaged_distance_pair_oddball)
```


```{r}
standardized_oddball <- odd_ball %>%
  group_by(subject_id, pair_type, pair, is_rel) %>%
  mutate(top = distance == .33) %>%
  mutate(next_change = if_else(correct == 1, -1, 1)) %>% 
  mutate(next_change = if_else(next_change == 1 & top, 0, next_change)) %>% 
  mutate(dist_change = cumsum(next_change))
```

```{r}
# Standardized distance change in steps by trial
stand_averaged_distance_oddball <- standardized_oddball %>% group_by(trial_number, pair_type, assigned_Condition) %>% summarise(dist_change = mean(dist_change)) %>% mutate(subject_id= ifelse(assigned_Condition=="control", "average_control", "average_exp"))

standardized_oddball %>% group_by(subject_id, pair_type, assigned_Condition) %>% ggplot(aes(x=trial_number, y=dist_change, group=subject_id, color=assigned_Condition)) + 
  geom_line(color="steelblue") + facet_grid(pair_type ~ .) + 
  geom_line(data=stand_averaged_distance_oddball)
```

```{r}
# Standardized distance change in steps, collasped over pair type, by trial
stand_averaged_distance_pair_oddball <- standardized_oddball %>% group_by(trial_number, pair, assigned_Condition) %>% summarise(dist_change = mean(dist_change)) %>% mutate(subject_id= ifelse(assigned_Condition=="control", "average_control", "average_exp"))

standardized_oddball %>% group_by(subject_id, pair, assigned_Condition) %>% ggplot(aes(x=trial_number, y=dist_change, group=subject_id, color=assigned_Condition)) + 
  geom_line(color="steelblue") + facet_grid(pair ~ .) + 
  geom_line(data=stand_averaged_distance_pair_oddball)
```

```{r}
#Standardized distance in steps, by block
stand_averaged_distance_oddball <- standardized_oddball %>% group_by(block, pair_type, assigned_Condition) %>% summarise(dist_change = mean(dist_change)) %>% mutate(subject_id= ifelse(assigned_Condition=="control", "average_control", "average_exp"))

block_stand_dist <- standardized_oddball %>% group_by(subject_id, assigned_Condition, pair_type, block) %>% summarize(dist_change = mean(dist_change)) 

block_stand_dist %>% group_by(subject_id, pair_type, assigned_Condition) %>% ggplot(aes(x=as.numeric(as.character(block)), y=dist_change, group=subject_id, color=assigned_Condition)) +
  geom_line(color="steelblue") + facet_grid(pair_type ~ .) + 
  geom_line(data=stand_averaged_distance_oddball)
```

```{r}
#Standardized distance in steps, by block collasped over pair type
stand_averaged_distance_pair_oddball <- standardized_oddball %>% group_by(block, pair, assigned_Condition) %>% summarise(dist_change = mean(dist_change)) %>% mutate(subject_id= ifelse(assigned_Condition=="control", "average_control", "average_exp"))

block_stand_pair_dist <- standardized_oddball %>% group_by(subject_id, assigned_Condition, pair, block) %>% summarize(dist_change = mean(dist_change)) 

block_stand_pair_dist %>% group_by(subject_id, pair, assigned_Condition) %>% ggplot(aes(x=as.numeric(as.character(block)), y=dist_change, group=subject_id, color=assigned_Condition)) +
  geom_line(color="steelblue") + facet_grid(pair ~ .) + 
  geom_line(data=stand_averaged_distance_pair_oddball)
```

Number judgement
```{r}
number_judge_average <- number_judge %>% group_by(block, pair_type) %>% summarise(prop_correct = mean(as.numeric(as.character(correct)))) %>% mutate(subject_id= "control")

number_judge_block <- number_judge %>% group_by(subject_id, pair_type, block) %>% summarise(prop_correct = mean(as.numeric(as.character(correct)))) 

number_judge_block %>% group_by(subject_id, pair_type) %>% ggplot(aes(x=as.numeric(as.character(block)), y=prop_correct, group=subject_id)) +
  geom_line(color="steelblue") + facet_grid(pair_type ~ .) + 
  geom_line(data=number_judge_average)
```
Category Judgement
```{r}
category_judge_average <- category_judge %>% group_by(block, pair_type) %>% summarise(prop_correct = mean(as.numeric(as.character(correct)))) %>% mutate(subject_id= "experimental")

category_judge_block <- category_judge %>% group_by(subject_id, pair_type, block) %>% summarise(prop_correct = mean(as.numeric(as.character(correct)))) 

category_judge_block %>% group_by(subject_id, pair_type) %>% ggplot(aes(x=as.numeric(as.character(block)), y=prop_correct, group=subject_id)) +
  geom_line(color="steelblue") + facet_grid(pair_type ~ .) + 
  geom_line(data=category_judge_average)
```

Just to explore, remove some of the worst participants (look at performance in final quarter)
```{r}
poor_number_judge <- number_judge %>% filter(as.numeric(as.character(block)) > 30) %>% group_by(subject_id) %>% summarize(prop_correct = mean(as.numeric(as.character(correct)))) %>% filter(prop_correct < .50) %>% select(subject_id)

poor_category_judge <- category_judge %>% filter(as.numeric(as.character(block)) >= 30) %>% group_by(subject_id) %>% summarize(prop_correct = mean(as.numeric(as.character(correct)))) %>% filter(prop_correct < .50) %>% select(subject_id)

poor_oddball <- standardized_oddball %>% filter(as.numeric(as.character(block)) > 30) %>% group_by(subject_id) %>% summarize(prop_correct = mean(as.numeric(as.character(correct)))) %>% filter(prop_correct < .50) %>% select(subject_id)

poor_oddball_overall_blocks <- standardized_oddball %>% filter(subject_id %in% poor_oddball$subject_id) %>% group_by(subject_id, block) %>% summarize(prop_correct = mean(as.numeric(as.character(correct))))
```


Worst guys over block
```{r}
poor_oddball_overall_blocks %>% ggplot(aes(x=as.numeric(as.character(block)), y= prop_correct, group=subject_id)) + geom_line()
```


Graph the oddball task again this time without worst guys
```{r}
stand_averaged_distance_oddball <-  standardized_oddball %>% filter(!(subject_id %in% poor_number_judge) && !(subject_id %in% poor_category_judge)) %>% group_by(block, pair_type, assigned_Condition) %>% summarise(dist_change = mean(dist_change)) %>% mutate(subject_id= ifelse(assigned_Condition=="control", "average_control", "average_exp"))

block_stand_dist <- standardized_oddball %>% filter(!(subject_id %in% poor_number_judge$subject_id) && !(subject_id %in% poor_category_judge$subject_id)) %>% group_by(subject_id, assigned_Condition, pair_type, block) %>% summarize(dist_change = mean(dist_change)) 

#pdf("DistanceChangeByBlockSepPairs.pdf")
distanceChangePairsSep <- block_stand_dist %>% group_by(subject_id, pair_type, assigned_Condition) %>% ggplot(aes(x=as.numeric(as.character(block)), y=dist_change, group=subject_id, color=assigned_Condition)) +
  scale_colour_manual(name="Legend", values=c("blue","darkorchid4","turquoise1", "pink1")) +
  geom_line() + facet_grid(. ~ pair_type) + 
  geom_line(data=stand_averaged_distance_oddball, aes(color=subject_id))
#print(distanceChangePairsSep)
#dev.off()
distanceChangePairsSep
```


```{r}
# Graph the pair types again without worst guys (for the oddball task)
stand_averaged_distance_pair_oddball_2 <- standardized_oddball %>% filter(!(subject_id %in% poor_oddball$subject_id)) %>% group_by(block, pair, assigned_Condition) %>% summarise(dist_change = mean(dist_change)) %>% mutate(subject_id= ifelse(assigned_Condition=="control", "average_control", "average_exp"))

block_stand_pair_dist_2 <- standardized_oddball %>% filter(!(subject_id %in% poor_oddball$subject_id)) %>% group_by(subject_id, assigned_Condition, pair, block) %>% summarize(dist_change = mean(dist_change)) 

#pdf("DistanceChangeByBlockRemovWorstOddball.pdf")
distanceChangeBlock2 <- block_stand_pair_dist_2 %>% group_by(subject_id, pair, assigned_Condition) %>% ggplot(aes(x=as.numeric(as.character(block)), y=dist_change, group=subject_id)) +
  scale_colour_manual(name="Legend", values=c("blue","darkorchid4","turquoise1", "pink1")) +
  geom_line(aes(color=assigned_Condition)) + facet_grid(pair ~ .) + 
  geom_line(data=stand_averaged_distance_pair_oddball_2, aes(color=subject_id)) + xlab("Block") + ylab("Standardized Distance Change")
#print(distanceChangeBlock2)
#dev.off()
distanceChangeBlock2
```

```{r}
# Graph the pair types again without worst guys
stand_averaged_distance_pair_oddball <-  standardized_oddball %>% filter(!(subject_id %in% poor_number_judge) && !(subject_id %in% poor_category_judge)) %>% group_by(block, pair, assigned_Condition) %>% summarise(dist_change = mean(dist_change)) %>% mutate(subject_id= ifelse(assigned_Condition=="control", "average_control", "average_exp"))

block_stand_pair_dist <- standardized_oddball %>% filter(!(subject_id %in% poor_number_judge$subject_id) && !(subject_id %in% poor_category_judge$subject_id)) %>% group_by(subject_id, assigned_Condition, pair, block) %>% summarize(dist_change = mean(dist_change)) 

#pdf("DistanceChangeByBlock.pdf")
distanceChangeBlock <- block_stand_pair_dist %>% group_by(subject_id, pair, assigned_Condition) %>% ggplot(aes(x=as.numeric(as.character(block)), y=dist_change, group=subject_id)) +
  scale_colour_manual(name="Legend", values=c("blue","darkorchid4","turquoise1", "pink1")) +
  geom_line(aes(color=assigned_Condition)) + facet_grid(. ~ pair) + 
  geom_line(data=stand_averaged_distance_pair_oddball, aes(color=subject_id)) + xlab("Block") + ylab("Standardized Distance Change")
#print(distanceChangeBlock)
#dev.off()
distanceChangeBlock
```

Creating groups based on levels of performance in task. Can change the thresholds
```{r}
number_judge_performance <- number_judge %>% group_by(subject_id, assigned_Condition) %>% summarize(prop_correct = mean(as.numeric(as.character(correct)))) %>% mutate(task_perf = case_when(
  # organized by quartile, first being border for lowest and third for the border of medium group
  prop_correct < .70 ~ "low", 
  prop_correct < .90 ~ "med",
  TRUE ~ "high"
)) %>% select(subject_id, task_perf)

category_judge_performance <- category_judge %>% group_by(subject_id, assigned_Condition) %>% summarize(prop_correct = mean(as.numeric(as.character(correct)))) %>% mutate(task_perf = case_when(
  # organized by quartile, first being border for lowest and third for the border of medium group
  prop_correct < .56 ~ "low",
  prop_correct < .79 ~ "med",
  TRUE ~ "high"
)) %>% select(subject_id, task_perf)

#Create single table of performance
task_performance <- rbind(number_judge_performance, category_judge_performance)
```

```{r}
standardized_oddball <- merge(standardized_oddball, task_performance, by="subject_id")
```

```{r}
# Graph each performance level
stand_averaged_distance_performance_oddball <- standardized_oddball %>% group_by(block, pair, assigned_Condition, task_perf) %>% summarise(dist_change = mean(dist_change)) %>% mutate(subject_id=paste(assigned_Condition, task_perf))

#pdf("DistanceChangeSepByTaskPerformance.pdf", width=10, height=6)
distanceChangeBlockByTaskPerformance <- stand_averaged_distance_performance_oddball %>% group_by(subject_id, pair, assigned_Condition) %>% ggplot(aes(x=as.numeric(as.character(block)), y=dist_change, group=subject_id, color=assigned_Condition)) +
  scale_colour_manual(name="Experimental Condition", values=c("blue","green")) +
  geom_line() + facet_grid(task_perf ~ pair) + xlab("Block") + ylab("Standardized Distance Change")
#print(distanceChangeBlockByTaskPerformance)
#dev.off()
distanceChangeBlockByTaskPerformance
#table(stand_averaged_distance_performance_oddball$task_perf)
```

How to evaluate graphically is there a relationship between doing better on the single task and the category task

Create dfs for proportion correct per pair type per block and compare to proportion correct per other task per block
```{r}
# Looking at just performance on this block, irrespective of where you start
subject_oddball_block_perf <- standardized_oddball %>% group_by(block, subject_id, pair, assigned_Condition) %>% summarise(av_distance = mean(next_change))

subject_category_block_perf <- category_judge %>% group_by(subject_id, block, assigned_Condition) %>% summarize(prop_correct = mean(as.numeric(as.character(correct))))
subject_number_block_perf <- number_judge %>% group_by(subject_id, block, assigned_Condition) %>% summarize(prop_correct = mean(as.numeric(as.character(correct))))

subject_task_block_perf <- rbind(subject_category_block_perf, subject_number_block_perf)

block_pair <- left_join(subject_oddball_block_perf, subject_task_block_perf, by=c("subject_id", "block", "assigned_Condition"))
```

Graph looking at if there is a relationship between doing well in the block on the cat/num judgement task and then doing well on the oddball task
```{r}
block_pair %>% group_by(subject_id, pair) %>% ggplot(aes(x=prop_correct, y=av_distance, group=assigned_Condition)) + facet_grid(pair ~ .) + geom_point() + geom_smooth(method='lm', aes(color=assigned_Condition))
# One subject only had 5 trials for blocks 38, 35
# missing 36 37: 5b7a902e16aa440001697f84

# Further investigation revealed that this person is the only who had this problem
```

Graph relevant vs irrelevant
```{r}
# Graph the pair types again without worst guys
stand_averaged_distance_rel_oddball <-  standardized_oddball %>% filter(!(subject_id %in% poor_number_judge) && !(subject_id %in% poor_category_judge)) %>% group_by(block, is_rel, assigned_Condition) %>% summarise(dist_change = mean(dist_change)) %>% mutate(subject_id= ifelse(assigned_Condition=="control", "average_control", "average_exp"))

block_stand_rel_dist <- standardized_oddball %>% filter(!(subject_id %in% poor_number_judge$subject_id) && !(subject_id %in% poor_category_judge$subject_id)) %>% group_by(subject_id, assigned_Condition, is_rel, block) %>% summarize(dist_change = mean(dist_change)) 

#pdf("DistanceChangeByBlockRel.pdf")
distanceChangeBlockRel <- block_stand_rel_dist %>% group_by(subject_id, is_rel, assigned_Condition) %>% ggplot(aes(x=as.numeric(as.character(block)), y=dist_change, group=subject_id)) +
  scale_colour_manual(name="Legend", values=c("blue","darkorchid4","turquoise1", "pink1")) +
  geom_line(aes(color=assigned_Condition)) + facet_grid(. ~ is_rel) + 
  geom_line(data=stand_averaged_distance_rel_oddball, aes(color=subject_id)) + xlab("Block") + ylab("Standardized Distance Change")
#print(distanceChangeBlock)
#dev.off()
distanceChangeBlockRel
```

Exclusion Criteria:
-people who did not exceed 50% accuracy in the final quarter
-people whose overall accuracy did not exceed some threshold
-keep everyone and organize into group based on performance
  - organize into groups by quartile
  - organize into low and high
- keep everyone but use performance on other task as something that factors into the model


Different analysis ideas:
- linear reg hierachical model to predict distance change using assigned condition and pair
    - use block
    - use trial number
    _ + add level of performance on other task (groups)
- evaluate just final distance change between groups (this is what we would normally do)


Potential model (ignoring cat performance)
```{r include=FALSE}
condition_model <- lme(dist_change ~ trial_number + assigned_Condition + pair+ pair*assigned_Condition, data=standardized_oddball, random=~trial_number|subject_id,  method="ML")
summary(condition_model)
```


